基于 LSTM 的视频配乐智能分类系统的研究与开发

### 2020-06-04 paper/paper.tex
feat: update paper and model (#3)
* Update paper.tex

* paper: normalize format

* feat: change genre categories

* paper: update

* fix: merge accordion into brass

* paper: knn and acknowledgement

* paper: hopefully final update

* paper: pdf metadata

* docs: add fetch model instructions

Co-authored-by: Luke X. Li <lixinyi@rdfzsu.org>

\documentclass[a4paper,utf8,10pt]{article}
\usepackage[UTF8]{ctex}
\usepackage{hyperref, geometry, fontspec, fancyhdr, scalefnt, minted, caption, cite, wrapfig, graphicx}
\usepackage[affil-it]{authblk}

>>>>

\documentclass[a4paper,utf8,10pt]{article}
\usepackage[UTF8]{ctex}
\usepackage{geometry, fontspec, fancyhdr, scalefnt, minted, caption, cite, wrapfig, graphicx}
\usepackage[pdfauthor={梁亚伦, 吴轩南, 李信义; 指导教师: 卢婧华, 武迪},
            pdftitle={基于LSTM的视频配乐智能分类系统的研究与开发},
            pdfsubject={中国人民大学附属中学研究性学习, 2020年},
            pdfkeywords={情绪识别;乐器识别;音频分类;视频配乐}]{hyperref}
\usepackage[affil-it]{authblk}
